Trajectories

### 2021-09-15 Rmd/report.Rmd
Add GitHub dark theme

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = TRUE,
  echo = FALSE,
  warning = TRUE,
  dev.args = list(png = list(type = "cairo")),
  include = TRUE,
  out.width = "100%",
  results = "asis",
  dpi = 300
)
options(
  knitr.kable.NA = "-",
  knitr.duplicate.label = "allow",
  ggplot2.discrete.fill = wesanderson::wes_palettes$Darjeeling1,
  ggplot2.discrete.colour = wesanderson::wes_palettes$Darjeeling1,
  ggplot2.continuous.fill = ggplot2::scale_color_gradient,
  ggplot2.continuous.colour = ggplot2::scale_color_gradient
)

@@

$$
\begin{aligned}
\color{white}
\log(\frac{p}{n - q}) &= (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
& (\beta_{1} + \beta_{1p})\times Cognate_{pi} + ... \\
& (\beta_{2} + \beta_{2i}) \times Exposure_{pi} + ... \\
& (\beta_{3} + \beta_{3i} + \beta_{3p}) \times (Cognate_{pi} \times Exposure_{pi}) + ... \\
& (\beta_{4} + \beta_{4i}) \times Age_{pi} + ... \\
& (\beta_{4} + \beta_{4p}) \times Frequency_{pi} + ... \\
& \varepsilon_{pi}
\end{aligned}
$$

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = TRUE,
  echo = FALSE,
  warning = TRUE,
  dev.args = list(png = list(type = "cairo")),
  include = TRUE,
  out.width = "80%",
  results = "asis",
  dpi = 250
)
options(
  knitr.kable.NA = "-",
  knitr.duplicate.label = "allow",
  ggplot2.discrete.fill = wesanderson::wes_palettes$Darjeeling1,
  ggplot2.discrete.colour = wesanderson::wes_palettes$Darjeeling1,
  ggplot2.continuous.fill = ggplot2::scale_color_gradient,
  ggplot2.continuous.colour = ggplot2::scale_color_gradient
)

@@

$$
\begin{aligned}
\color{white}\log(\frac{p}{n - q}) &= (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
& \color{white}(\beta_{1} + \beta_{1p})\times Cognate_{pi} + ... \\
& \color{white}(\beta_{2} + \beta_{2i}) \times Exposure_{pi} + ... \\
& \color{white}(\beta_{3} + \beta_{3i} + \beta_{3p}) \times (Cognate_{pi} \times Exposure_{pi}) + ... \\
& \color{white}(\beta_{4} + \beta_{4i}) \times Age_{pi} + ... \\
& \color{white}(\beta_{4} + \beta_{4p}) \times Frequency_{pi} + ... \\
& \color{white}\varepsilon_{pi}
\end{aligned}
$$
